---
title: "HW1"
author: "Kerin Grewal"
date: "Jan 21st"
output: 
  pdf_document:
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##1. Create the vecors:
###(a) (1, 2, 3, . . . , 19, 20)

```
##  [1]  1  2  3  4  5  6  7  8  9 10 11 12 13 14 15 16 17 18 19 20
```

###(b) (20, 19, . . . , 2, 1)
```{r echo= FALSE}
y <- seq(20, 1, -1)
y
```

###(c) (1, 2, 3, . . . , 19, 20, 19, 18, . . . , 2, 1)
```{r echo= FALSE}
c(1:20, 19:1)
```

###(d) (4, 6, 3) and assign it to the name tmp.
```{r echo= FALSE}
tmp <- c(4, 6, 3)
tmp
```

###(e) (4, 6, 3, 4, 6, 3, . . . , 4, 6, 3) where there are 10 occurrences of 4.
```{r echo= FALSE}
b <- rep(tmp, 10)
b
```

###(f) (4, 6, 3, 4, 6, 3, . . . , 4, 6, 3, 4) where there are 11 occurrences of 4, 10 occurrences of 6 and 10 occurrences of 3.
```{r echo= FALSE}
a <- rep(tmp, length = 31)
a
```

###(g) (4, 4, . . . , 4, 6, 6, . . . , 6, 3, 3, . . . , 3) where there are 10 occurrences of 4, 20 occurrences of 6 and 30 occurrences of 3.
```{r echo= FALSE}
c = c(rep(4, 10), rep(6, 20), rep(3, 30))
c
```

##2. Create a vector of the values of e^x cos(x) at x = 3, 3.1, 3.2, . . . , 6.
```{r echo= FALSE}
x <- seq(3, 6, by = 0.1)
v <- exp(x) * cos(x)
v
```

##3. Create the following vectors:
###(a) (0.1^3, 0.2^1, 0.1^6, 0.2^4, . . . , 0.1^36, 0.2^34)
```{r echo= FALSE}
x <- seq(3, 36, by = 3)
y <- seq(1, 34, by = 3)
v <- 0.1 ^ (x) * 0.2 ^ (y)
v
```

###(b)
```{r echo= FALSE}
x <- seq(2, 25)
v <- 2^x/x
v
```

##4. Calculate the following:
###(a)
```{r echo= FALSE}
i <- c(10:100)
v <- sum(i^3 + 4 * i^2)
v
```

###(b)
```{r echo= FALSE}
i = c(1: 25)
v = sum((2^i/ i)+(3^i/ i^2))
v
```

##5. Use the function paste to create the following character vectors of length 30:
###(a) ("label 1", "label 2", ....., "label 30").
```{r echo= FALSE}
a <- paste("label", 1:30, sep = " ")
a
```

###(b) ("fn1", "fn2", ..., "fn30").
```{r echo= FALSE}
b <- paste("fn", 1:30, sep= "")
b
```

##6. Execute the following lines which create two vectors of random integers which are chosen with replacement from the integers 0, 1, . . . , 999. Both vectors have length 250.

###(a) Create the vector (y2 − x1, . . . , yn − xn−1).
```{r echo= FALSE}
set.seed(50)
xVec <- sample(0:999, 250, replace=T)
yVec <- sample(0:999, 250, replace=T)
a <- yVec[-1] - xVec[-length(xVec)]
a
```

###(b)
```{r echo= FALSE}
b <- sin(yVec[-length(yVec)]) / cos(xVec[-1])
b
```

###(c) Create the vector (x1 + 2x2 − x3, x2 + 2x3 − x4, . . . , xn−2 + 2xn−1 − xn).
```{r echo= FALSE}
c <- xVec[1:248] + 2 * xVec[2:249] - xVec[3:250]
c
```

###(d)
```{r echo= FALSE}
e <- exp(1)
i <- 1: 249
d <- sum(e^(-xVec[-1] / xVec[-length(xVec)] + 10))
d
```

##7. This question uses the vectors xVec and yVec created in the previous question and the functions sort, order, mean, sqrt, sum and abs.
###(a) Pick out the values in yVec which are > 600.
```{r echo= FALSE}
vals <- yVec[yVec>600]
vals
```

###(b) What are the index positions in yVec of the values which are > 600?
```{r echo= FALSE}
p <- which(yVec>600)
p
```

###(c) What are the values in xVec which correspond to the values in yVec which are > 600? (By correspond, we mean at the same index positions.)
```{r echo= FALSE}
vals <- xVec[yVec>600]
vals
```


###(d)
```{r echo= FALSE}
vals <- sqrt(abs(xVec-mean(xVec)))
vals
```


###(e) How many values in yVec are within 200 of the maximum value of the terms in yVec?
```{r echo= FALSE}
vals <- sum(abs(xVec-mean(xVec)))
vals
```

###(f) How many numbers in xVec are divisible by 2? (Note that the modulo operator is denoted %%.)
```{r echo= FALSE}
vals <- sum(xVec%%2 ==0)
vals
```


###(g) Sort the numbers in the vector xVec in the order of increasing values in yVec.
```{r echo= FALSE}
vals <- xVec[order(yVec)]
vals
```


###(h) Pick out the elements in yVec at index positions 1, 4, 7, 10, 13, . . . .
```{r echo= FALSE}
vals <- yVec[c(T, F, F)]
vals
```


##8. By using the function cumprod or otherwise, calculate
```{r echo= FALSE}
vals <- 1+sum(cumprod(seq(2, 38, by=2)/ seq(3, 39, by= 2)))
vals
```